---
title: "Who is faster up and down"
author: "Carlos Campos"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
source("bootstrap.R")
```

# Introduction
Q3. differences between time up and down the stairs between guys and gals. 
In the next set of data, we will decide if $H_0$ the time for guys and gals going up and down the stairs is the same.

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
We start by loading the data into 2 data frames

```{r}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```
```{r}
write.csv(x=alldat,file="alldat.csv")
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
we use graphical dscriptions suchs as a box plot and numerical summaries.

#Results
the different tests conducted show a sligth difference between gays and gals going up the stairs. Gays go up and down slighly faster than gals with 6 seconds in differences (gals 30-24 guys).


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
In this section, a box plot is showing the differences in time that guys and gals take in   going up and down the stairs. The black line in the middle of the boxes shows the average   period that takes them to go up and down the stairs. it takes approximately 30 seconds for   gals to go up and down the stairs and it takes approximately 24 seconds for guys to go up and down the stairs. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
Boxplot(time_down_up~Gender, data=alldat, id=list(method="y"))
```
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
numSummary(alldat[,"time_down_up", drop=FALSE], groups=alldat$Gender, 
  statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```

  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
We will run a t-test to test this hypothesis. 

$H_0$ The average time to go up and down the stairs is the same between guys and gals.  
$H_a$ The average time is different between guys and gals in going up and down the stairs.

```{r}
t.test(time_down_up~Gender, alternative='two.sided', conf.level=.95, var.equal=FALSE, 
  data=alldat)
```
```{r}
a <- na.omit(alldat$time_down_up[ which(alldat$Gender=='F')])
b <- na.omit(alldat$time_down_up[ which(alldat$Gender=='M')])
bs=bootstrp (a,b,1000)
```


  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
there's a difference in time between guys and gals going up and down the stairs the p     value=0.01116 shows significance and the Hyphotesis; $H_0$ The average time to go up and down the stairs is the same between guys and gals is rejected. in conculsion, the data use in the different test shows a difference between guys and gals going up and down the stairs guys having an avarage peiod time of 24 seconds and gals and having an avarage perido time of 30 seconds up and down the stairs.



